CommonMind Consortium: DLPFC

### 2020-09-16 combined_analysis/combine_all_DLPFC.Rmd
bug fixes

@@

# Compute residuals, but add back in Dx*Reported_Gender
f = function(fit){
  residuals(fit) + get_prediction( fit, ~ Dx*Reported_Gender)
}

@@

  # Compute residuals which adding back Diagnosis and Sex effects
  resid.lst = fitVarPartModel(vobj, form_use, info, fxn = f, BPPARAM = SnowParam(18))  
  do.call(rbind, resid.lst)
  })
names(residuals.lst) = names(vobj.lst)
```

>>>>

```{r corr.matrix}
form = Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*(ageOfDeath + cellFrac_ilr_1 + cellFrac_ilr_2 + cellFrac_ilr_3),

@@

eval_residuals = function( form ){
  # Compute residuals, but add back in Dx*Reported_Gender
  # for form = ~ Dx*Reported_Gender
  f = function(fit){
    residuals(fit) + get_prediction( fit, form)
  }

@@

    # Compute residuals which adding back Diagnosis and Sex effects
    resid.lst = fitVarPartModel(vobj, form_use, info, fxn = f, BPPARAM = SnowParam(18))  
    do.call(rbind, resid.lst)
    })
  names(residuals.lst) = names(vobj.lst)

  residuals.lst
}

resid.add = list( Dx_Sex  = eval_residuals( ~ Dx*Reported_Gender ),
                  Dx      = eval_residuals( ~ Dx ),
                  Sex     = eval_residuals( ~ Reported_Gender ))
```
